---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(poweRof10)
library(tidyverse)
```

# poweRof10

<!-- badges: start -->
![](https://img.shields.io/badge/just-for%20fun-blue.svg) [![R build status](https://github.com/hfshr/poweRof10/workflows/R-CMD-check/badge.svg)](https://github.com/hfshr/poweRof10/actions)
![stability-wip](https://img.shields.io/badge/stability-work_in_progress-lightgrey.svg)
<!-- badges: end -->

`poweRof10` is a small package that scrapes data from athletics rankings website www.thepowerof10.info. I'm a big athletics fan and created `poweRof10` for a bit of fun to analyse my own performances, but thought it might be worth sharing here. The package is still a little rough around the edges, but the basic functionality should work well enough!

Check out [this blog post](https://hfshr.xyz/posts/2020-10-22-introducing-powerof10/) for some more examples.

## Installation

Install from github with:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("hfshr/poweRof10")
```

## Basic usage

You can get the rankings for a specific event/year/gender/age group using the `get_event()` function:

```{r}
get_event(event = "100", agegroup = "ALL", gender = "M", year = 2016, top_n = 10) %>% 
  select(rank, perf, name, venue)
```

Alternatively, you can search for an individual athlete and get their performance history with `get_athlete()`:

```{r}
get_athlete(fn = "Harry", sn = "Fisher", club = "Cardiff/Cardiff Met Uni") %>% 
  select(event, perf, pos, venue, date) %>% 
  head(10)
```

## Acknowledgements

Thanks to the team that keep www.thepowerof10.info up and running, it's an invaluable resource for many!

## Disclaimer

This software is in no way affiliated, endorsed, or approved by www.thepowerof10.info or any of its affiliates.


